Holomorphic field theories and higher algebra

### 2022-07-11 draft.tex
added subsections to fill in

The mathematical motivation is simple:
for most classical holomorphic field theories, the solutions to the equations of motion form a moduli space of natural interest to complex geometers,
and it is natural to hope that its quantization is equally interesting.
A well-known example is holomorphic Chern-Simons theory,
which lives on a Calabi-Yau 3-fold $X$ and involves the {\em derived} moduli space $\RR\Bun_G(X)$ of holomorphic principal $G$-bundles on $X$.
Other classes of examples are afforded by holomorphic variants of familiar AKSZ $\sigma$-models; the relevant moduli space being the derived mapping space between complex manifolds.

@@

@@

>>>>

The mathematical motivation is simple:
for most classical holomorphic field theories, the solutions to the equations of motion form a moduli space of natural interest to complex geometers,
and it is natural to hope that its quantization is equally interesting.
A well-known example is holomorphic Chern-Simons theory,
which lives on a Calabi-Yau 3-fold $X$ and involves the {\em derived} moduli space $\RR\Bun_G(X)$ of holomorphic principal $G$-bundles on $X$.
As a somewhat mundane example, let $\RR\Hol(X,V)$ denote the derived moduli space of holomorphic maps from some complex manifold $X$ to another complex manifold $V$.
(For $V$ a vector space, a ``derived'' enhancement is familiar as the higher dimensional cohomology $H^*(X, \cO) \otimes V$.)
One can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,
and this derived moduli space encodes solutions to
a theory known as the $\beta\gamma$ system with target $V$.
(The name is silly: it's due to the original notation people used.)
Every question one asks about the classical physics of the $\beta\gamma$ theory translates into a question about this moduli space.
Other classes of examples are afforded by holomorphic variants of familiar AKSZ $\sigma$-models; the relevant moduli space being the derived mapping space between complex manifolds.

@@

\subsection{Reduction vs chiralization}

\owen{We should introduce the idea here and revisit later}

@@

\subsection{Toric (KK) reduction vs. chiralization}

\owen{revisit this theme, and discuss the "modes" algebra}

\subsection{Operator product expansion and holomorphic Poisson algebras}

\owen{discuss OPE and explain the shifted Poisson structure}
